### 2018-12-26 mycv/subs/papers.tex
Updates

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {H. Kim, F Barlat, Y. Lee, S. Zaman, CS Lee, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1016/j.ijplas.2018.07.010}{A crystal plasticity model for describing the anisotropic hardening behavior of steel sheets during strain-path changes}}
  {International Journal of Plasticity}
  {In press}
  {
  }

@@

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
\item
  \cventry
  {\underline{Y. Jeong}, T. Manninen}
  {\href{https://doi.org/10.1088/1742-6596/1063/1/012020}{Formability predictions and measurement of 316L stainless steel using self-consistent crystal plasticity}}
  {Journal of Physics: Conference Series}
  {Vol. 1063, 2018}
  {
  }

  \cventry
  {\underline{Y. Jeong}, S. Panich}
  {\href{https://doi.org/10.1016/j.promfg.2018.07.209}{Forming limits of dual phase steels using crystal plasticity in conjunction with MK approach}}
  {Procedia Manufacturing}
  {Vol. 15, 1816-1824, 2018}
  {
  }

>>>>

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
    % ---------------------------------------------------------
  % ---------------------------------------------------------
  \cventry
  {H. Kim, F Barlat, Y. Lee, S. Zaman, CS Lee, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1016/j.ijplas.2018.07.010}{A crystal plasticity model for describing the anisotropic hardening behavior of steel sheets during strain-path changes}}
  {International Journal of Plasticity}
  {Vol. 111 p85-106, 2018}
  {
  }

@@

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
\item
    \cventry
  {\underline{Y. Jeong}$^*$, Timo Manninen}
  {\href{http://iopscience.iop.org/article/10.1088/1742-6596/1063/1/012020}{Formability predictions and measurement of 316L stainless steel using self-consistent crystal plasticity}}
  {Journal of Physics: Conference Series}
  {Vol. 150673, 2018}
  {
  }

  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, S. Panich}
  {\href{https://doi.org/10.1016/j.promfg.2018.07.209}{Forming limits of dual phase steels using crystal plasticity in conjunction with MK approach}}
  {Procedia Manufacturing}
  {Vol. 15, 2018}
  {
  }
